Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-05-22 Paper Sigatoka - 2015.tex
22 mayo 2016

@@

In this work, we compare five machine learning techniques 
to predict the development rate of the black Sigatoka disease:
support
vector regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression.
%
The main contribution of this work is a comparison between machine
learning methods to forecast black Sigatoka development rate. 
\marginnote{FALTA COMPLETAR esta parte}

The outline of the paper is as follows. In Section 2, we present materials and methods of our research. In Section 3, we present the main results and their discussion. Our conclusions and future work are presented in Section 4.

\section{Materials and methods}

\subsection{Concepts}

\subsubsection{Black Sigatoka disease}

The black Sigatoka is a disease caused by the fungus
\emph{Mycosphaerella fijiensis Morelet}.  It is the main
phytopathologic problem of banana and plantain crops in Central
America \citep{MarinVargas1995}.
%
This disease attacks the plant leaves producing a rapid deterioration
of the leaf area. It affects the growth and productivity of the
affected plant by impairing its photosynthetic capacity, which
consequently causes a reduction in quality of the fruit
\citep{MarinVargas1995}.

\subsubsection{Biological warning system}

\TODO{ LISTO  Revisar si la nueva redacción de este párrafo coincide con la
  original.  Eso es lo que creo se quería decir, porque no quedaba
  claro cuál sistema fue creado por quién...  Las referencias a cada
  sistema en algo así son absolutamente necesarias.  Favor reemplazar
  {XXX} por las referencias correspondientes (Pablo, 1/5/16)}

The latter system is based on weekly quantified observations of
the disease progression on young leaves of the plant, according to
Fouré's scale of the symptom stages.
%
The numeric coefficients describe the degree of incidence and the
severity of the disease development.  These coefficients are used to
calculate two variables: gross sum and state of evolution.

\TODO{ EN REALIDAD ASÍ ES USADO EN EL TEXTO FUENTE
coefficients??  No suena como coeficientes (un factor que
  multiplica términos en una función) sino como una calificación o
  nota o algo así (quizá ``grade''?).  ``Arbitrary coefficient'' no
  tiene sentido por el ``arbitrary''... No creo que sean tan
  arbitrarios sino predefinidos.  De hecho, el párrafo que sigue dice
  que suben con el avance de síntomas, es decir, no es tan
  ``arbitrario''.  Quizá querés decir ``arbitrarily chosen''?.  No
  estoy seguro si entiendo lo que se quiere decir aquí.}

\subsubsection{Support Vector Regression (SVR)}

@@

\subsubsection{Ordinary least squares regression}
This method fits a linear model with coefficients $w = (w1,..,wp)$ to minimize the residual sum of squares between the observed responses in the dataset, and the responses predicted by the linear approximation. Mathematically it solves a problem of the form \citep{scikitlearn2011}:
$$\min_{w} \Bigr| \Bigr| Xw - y \Bigr| \Bigr|_2^2  $$
where $X$ denotes the features matriz. \\
According Pedregosa et al. \citep{scikitlearn2011}  the coefficient estimates for Ordinary Least Squares rely on the independence of the model terms. When terms are correlated and the columns of the design matrix $X$ have an approximate linear dependence, the design matrix becomes close to singular and as a result, the least-squares estimate becomes highly sensitive to random errors in the observed response, producing a large variance. This situation of multicollinearity can arise, for example, when data are collected without an experimental design

\subsubsection{Ridge regression}
The ridge regression addresses some of the problems of ordinary least squares regression by imposing a penalty on the size of the coefficients. The ridge coefficients minimize a penalized residual sum of squares  \citep{scikitlearn2011}:

@@

\subsubsection{Elastic-Net regression}
Elastic-Net is a linear regression model trained with $L1$ and $L2$ prior as regularizer. This combination allows for learning a sparse model where few of the weights are non-zero like Lasso, while still maintaining the regularization properties of Ridge  \citep{scikitlearn2011}. The convex combination of $L1$ and $L2$ is controled by using the $l1_{ratio}$ parameter.

@@

\subsubsection{Echo State Networks (ESN)}
Recurrent Neural Networks (RNN) are useful for temporal patterns, but when they are trained with backpropagation methods, they are very slow.  Echo State Network (ESN) is an alternative training method to solve that problem.  ESN is based on the observation that if a random RNN possesses certain algebraic properties, training only a linear readout from it is often sufficient to achieve excellent performance in practical applications \citep{Lukose2009}. 
For a given training input signal $u(n)  \in R^{N_u}$ a desired target output signal $y^{target}(n) \in R^{N_y}$
is known. Here $n = 1, . . . ,T$ is the discrete time and $T$ is the number of data points in the training dataset. The task is to learn a model with output $y(n) \in R^{N_y}$, where $y(n)$ matches $y^target(n)$ as well as possible, minimizing an error measure $E(y,y^target)$, and, more importantly, generalizes well to unseen data. The untrained RNN part of an ESN is called a dynamical reservoir, and the resulting states x(n) are termed echoes of its input history \citep{Lukose2012}. Finally, these signals are sent to an output layer as shown in the \figurename
$.$\ref{figura3}.
\begin{figure}[h] 
 \centering
 \includegraphics[scale=.9]{Reservorio}
 \caption{An echo state network \citep{Lukose2012}.} 
 \label{figura3} 
\end{figure}

@@

\subsubsection{Related works}
Huang et al. \citep{Huang2010}  surveyed the development of soft computing techniques in agricultural and biological engineering, including fuzzy logic, artificial neural networks, genetic algorithms, bayesian inference and decision trees.

@@

\subsubsection{Data}
In this work we use data acquired in two research farms of Corbana in Costa Rica: 1) 28 Millas (previously called Waldeck and located at Matina) and La Rita (located at Pococí), both in the province of Limón, Costa Rica. The banana type is Musa AAA, subgroup Cavendish, cv. Grande Naine. The \tablename $.$\ref{tabla1} shows the variables available.

@@

\subsubsection{Data preprocessing}

@@

\subsection{Methodology}
The selection of methods and their parametrisation was performed in two stages.

@@

This second phase intents to expose how these methods behave on a considerable climate in the years 2014 and 2015.
\marginnote{Poner una cita que fundamente este ultimo parrafo}

@@

In this section we present the main results for phase.

>>>>

\TODO{ CORREGIDO (LUIS-ALEX)
revisar si la nueva redacción de este párrafo coincide con la
  original.  Eso es lo que creo se quería decir, porque no quedaba
  claro cuál sistema fue creado por quién...  Las referencias a cada
  sistema en algo así son absolutamente necesarias.  Favor reemplazar
   por las referencias correspondientes (Pablo, 1/5/16)}

This bilogical warning system is based on weekly quantified observations of the disease progression on young leaves of the plant, according to
Fouré's scale of the symptom stages. The numeric coefficients describe the degree of incidence and the severity of the disease development.  These coefficients are used to
calculate two variables: gross sum and state of evolution.

\TODO{ EN REALIDAD ASÍ ES USADO EN EL TEXTO FUENTE EN INGLÉS (LUIS ALEX)
coefficients??  No suena como coeficientes (un factor que
  multiplica términos en una función) sino como una calificación o
  nota o algo así (quizá ``grade''?).  ``Arbitrary coefficient'' no
  tiene sentido por el ``arbitrary''... No creo que sean tan
  arbitrarios sino predefinidos.  De hecho, el párrafo que sigue dice
  que suben con el avance de síntomas, es decir, no es tan
  ``arbitrario''.  Quizá querés decir ``arbitrarily chosen''?.  No
  estoy seguro si entiendo lo que se quiere decir aquí.}

@@

In this work, we compare five machine learning techniques 
to predict the development rate of the black Sigatoka disease:
support
vector regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression.
%
The main contribution of this work is the selection of the best machine learning technique to forecast the black Sigatoka development rate according to the metric indicated below.

The outline of the paper is as follows. In Section 2, we introduce the machine learning techniques used in this research and the main related works. In section 3, we present the data used and the methodology for the study results. In section 4, we present the results and their discussion. Our conclusions and future work are presented in Section 5.

\section{Machine learning techniques and Related works}
In this section we summary the machine learning techniques used and we present the main related works.

\subsection{Support Vector Regression (SVR)}

@@

\subsection{Ordinary least squares regression}
This method fits a linear model with coefficients $w = (w1,..,wp)$ to minimize the residual sum of squares between the observed responses in the dataset, and the responses predicted by the linear approximation. Mathematically it solves a problem of the form \citep{scikitlearn2011}:
$$\min_{w} \Bigr| \Bigr| Xw - y \Bigr| \Bigr|_2^2  $$
where $X$ denotes the features matriz. \\
According Pedregosa et al. \citep{scikitlearn2011}  the coefficient estimates for Ordinary Least Squares rely on the independence of the model terms. When terms are correlated and the columns of the design matrix $X$ have an approximate linear dependence, the design matrix becomes close to singular and as a result, the least-squares estimate becomes highly sensitive to random errors in the observed response, producing a large variance. This situation of multicollinearity can arise, for example, when data are collected without an experimental design

\subsection{Ridge regression}
The ridge regression addresses some of the problems of ordinary least squares regression by imposing a penalty on the size of the coefficients. The ridge coefficients minimize a penalized residual sum of squares  \citep{scikitlearn2011}:

@@

\subsection{Elastic-Net regression}
Elastic-Net is a linear regression model trained with $L1$ and $L2$ prior as regularizer. This combination allows for learning a sparse model where few of the weights are non-zero like Lasso, while still maintaining the regularization properties of Ridge  \citep{scikitlearn2011}. The convex combination of $L1$ and $L2$ is controled by using the $l1_{ratio}$ parameter.

@@

\subsection{Echo State Networks (ESN)}
Recurrent Neural Networks (RNN) are useful for temporal patterns, but when they are trained with backpropagation methods, they are very slow.  Echo State Network (ESN) is an alternative training method to solve that problem.  ESN is based on the observation that if a random RNN possesses certain algebraic properties, training only a linear readout from it is often sufficient to achieve excellent performance in practical applications \citep{Lukose2009}. 
For a given training input signal $u(n)  \in R^{N_u}$ a desired target output signal $y^{target}(n) \in R^{N_y}$
is known. Here $n = 1, . . . ,T$ is the discrete time and $T$ is the number of data points in the training dataset. The task is to learn a model with output $y(n) \in R^{N_y}$, where $y(n)$ matches $y^target(n)$ as well as possible, minimizing an error measure $E(y,y^target)$, and, more importantly, generalizes well to unseen data. The untrained RNN part of an ESN is called a dynamical reservoir, and the resulting states x(n) are termed echoes of its input history \citep{Lukose2012}. Finally, these signals are sent to an output layer as shown in the \figurename
$.$\ref{figura3}.
\begin{figure}[h] 
 \centering
 \includegraphics[scale=.9]{Reservorio}
 \caption{An echo state network \citep{Lukose2012}.} 
 \label{figura3} 
\end{figure}

@@

\subsection{Related works}
Now, we present the main and recently works related with our study.

Huang et al. \citep{Huang2010}  surveyed the development of soft computing techniques in agricultural and biological engineering, including fuzzy logic, artificial neural networks, genetic algorithms, bayesian inference and decision trees.

@@

\section{Specification of data and methodology}
In this section, we present the data and how we worked to obtain our results.

\subsection{Data}
We use data acquired in two research farms of Corbana in Costa Rica: 1) 28 Millas (previously called Waldeck and located at Matina) and La Rita (located at Pococí), both in the province of Limón, Costa Rica. The banana type is Musa AAA, subgroup Cavendish, cv. Grande Naine. The \tablename $.$\ref{tabla1} shows the variables available.

@@

\subsection{Data preprocessing}
Usually, data need preprocessing to prepare for use. In this section we explain that process.

@@

\subsection{Methodology}
The selection of the technique and its parametrisation was performed in two stages that they are presented below.

@@

@@

In this section we present the main results for phase and their discussion.
